<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-11-02 MainAnalysis.Rmd
Making sure to separate media

```{r, run_invivoPKfit_2comp, eval = FALSE}
### do 2-Compartment fit
system.time(PK.fit.table.2comp <- fit_all(
  data.set = cvt.data,
  model = "2compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
    dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA,
  suppress.messages=TRUE
))
```

```{r, run_invivoPKfit_flat, eval = FALSE}
### do flat fit
system.time(PK.fit.table.flat <- fit_all(
  data.set = cvt.data,
  model = "flat",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
    dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.col ="calc_loq",
  subject.default = NA,
  info.default = NA,
  suppress.messages=TRUE
))
```

>>>>

```{r, run_invivoPKfit_2comp, eval = FALSE}
### do 2-Compartment fit
system.time(PK.fit.table.2comp <- fit_all(
  data.set = cvt.data,
  model = "2compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.col ="calc_loq",
  subject.default = NA,
  info.default = NA,
  suppress.messages = TRUE
))
```

```{r, run_invivoPKfit_flat, eval = FALSE}
### do flat fit
system.time(PK.fit.table.flat <- fit_all(
  data.set = cvt.data,
  model = "flat",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.col ="calc_loq",
  subject.default = NA,
  info.default = NA,
  suppress.messages = TRUE
))
```
